The low-frequency environment of the Murchison Widefield Array: radio-frequency interference analysis and mitigation

### 2014-11-26 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Fixed Bernardi's affiliation

\def\ANU{$^{1}$}
\def\CAASTRO{$^{2}$}
\def\ASTRON{$^{3}$}
\def\Curtin{$^{4}$}
\def\UWisc{$^{5}$}
\def\UW{$^{6}$}
\def\CASS{$^{7}$}
\def\SKASA{$^{8}$}
\def\ASU{$^{9}$}
\def\USydney{$^{10}$}
\def\Haystack{$^{11}$}
\def\RRI{$^{12}$}
\def\MIT{$^{13}$}
\def\UWA{$^{14}$}
\def\CfA{$^{15}$}
\def\Victoria{$^{16}$}
\def\UMelbourne{$^{17}$}
\def\Tata{$^{18}$}
%\def\UMichigan{$^{19}$}
%\def\NRAO{$^{20}$}

\author[A.~R.~Offringa et al.]{A.~R.~Offringa\ANU$^,$\CAASTRO$^,$\ASTRON\thanks{Corresponding author. E-mail: \url{offringa@gmail.com}},
R.~B.~Wayth\Curtin$^,$\CAASTRO,
N.~Hurley-Walker\Curtin,
D.~L.~Kaplan\UWisc,
N.~Barry\UW,
A.~P.~Beardsley\UW,
M.~E.~Bell\CASS$^,$\CAASTRO,
G.~Bernardi\SKASA,
J.~D.~Bowman\ASU, 
F.~Briggs\ANU$^,$\CAASTRO,
J.~R.~Callingham\USydney$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
%A.~de~Oliveira-Costa
A.~A.~Deshpande\RRI, 
J.~S.~Dillon\MIT,
K.~S.~Dwarakanath\RRI,
A.~Ewall-Wice\MIT,
L.~Feng\MIT,
B.-Q.~For\UWA,
B.~M.~Gaensler\USydney$^,$\CAASTRO, 
L.~J.~Greenhill\CfA,
P.~Hancock\Curtin$^,$\CAASTRO,
B.~J.~Hazelton\UW,
J.~N.~Hewitt\MIT,
L.~Hindson\Victoria,
D.~C.~Jacobs\ASU, 
M.~Johnston-Hollitt\Victoria,
A.~D.~Kapi\'{n}ska\UWA$^,$\CAASTRO,
H.-S.~Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
B.~McKinley\ANU$^,$\CAASTRO$^,$\UMelbourne,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
J.~Morgan\Curtin,
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
S.~Paul\RRI,
B.~Pindor\UMelbourne,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
N.~Udaya~Shankar\RRI, 
S.~Sethi\RRI,
K.~S.~Srivani\RRI,
L.~Staveley-Smith\UWA$^,$\CAASTRO,
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
N.~Thyagarajan\ASU,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
C.~Wu\UWA,
J.~S.~Wyithe\UMelbourne$^,$\CAASTRO,
Q. Zheng\Victoria
\\
\ANU{}Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia \\
%\CAASTRO{}ARC Centre of Excellence for All-sky Astrophysics, Australian National University, Canberra, ACT 2611, Australia \\
\CAASTRO{}ARC Centre of Excellence for All-sky Astrophysics (CAASTRO) \\
\ASTRON{}Netherlands Institute for Radio Astronomy (ASTRON), PO Box 2, 7990 AA Dwingeloo, The Netherlands\\
\Curtin{}International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
\UWisc{}Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA\\
\UW{}Department of Physics, University of Washington, Seattle, WA 98195, USA\\
\CASS{}CSIRO Astronomy and Space Science, Marsfield, NSW 2122, Australia\\
\SKASA{}Square Kilometre Array South Africa (SKA SA), Cape Town, 7405, South Africa\\
\ASU{}School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85287, USA\\
\USydney{}Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia\\
\Haystack{}MIT Haystack Observatory, Westford, MA 01886, USA\\
\RRI{}Raman Research Institute, Bangalore 560080, India\\
\MIT{}Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
\UWA{}ICRAR, University of Western Australia, Crawley, WA 6009, Perth, Australia\\
\CfA{}Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA\\
\Victoria{}School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand\\
\UMelbourne{}School of Physics, University of Melbourne, Parkville, VIC 3010, Australia\\
\Tata{}National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India
%\UMichigan{}University of Michigan, Ann Harbor, MI 48109, USA
}
\jid{PASA}
\doi{10.1017/pas.\the\year.xxx}
\jyear{\the\year}
%Citations may be made using the natbib commands \citet{},\citep{} etc.
\usepackage[authoryear]{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
\setlength{\bibsep}{0.3mm}

>>>>

\def\ANU{$^{1}$}
\def\CAASTRO{$^{2}$}
\def\ASTRON{$^{3}$}
\def\Curtin{$^{4}$}
\def\UWisc{$^{5}$}
\def\UW{$^{6}$}
\def\CASS{$^{7}$}
\def\SKASA{$^{8}$}
\def\Rhodes{$^{9}$}
\def\CfA{$^{10}$}
\def\ASU{$^{11}$}
\def\USydney{$^{12}$}
\def\Haystack{$^{13}$}
\def\RRI{$^{14}$}
\def\MIT{$^{15}$}
\def\UWA{$^{16}$}
\def\Victoria{$^{17}$}
\def\UMelbourne{$^{18}$}
\def\Tata{$^{19}$}
%\def\UMichigan{$^{19}$}
%\def\NRAO{$^{20}$}

\author[A.~R.~Offringa et al.]{A.~R.~Offringa\ANU$^,$\CAASTRO$^,$\ASTRON\thanks{Corresponding author. E-mail: \url{offringa@gmail.com}},
R.~B.~Wayth\Curtin$^,$\CAASTRO,
N.~Hurley-Walker\Curtin,
D.~L.~Kaplan\UWisc,
N.~Barry\UW,
A.~P.~Beardsley\UW,
M.~E.~Bell\CASS$^,$\CAASTRO,
G.~Bernardi\SKASA$^,$\Rhodes$^,$\CfA,
J.~D.~Bowman\ASU, 
F.~Briggs\ANU$^,$\CAASTRO,
J.~R.~Callingham\USydney$^,$\CAASTRO,
R.~J.~Cappallo\Haystack, 
P.~Carroll\UW,
%A.~de~Oliveira-Costa
A.~A.~Deshpande\RRI, 
J.~S.~Dillon\MIT,
K.~S.~Dwarakanath\RRI,
A.~Ewall-Wice\MIT,
L.~Feng\MIT,
B.-Q.~For\UWA,
B.~M.~Gaensler\USydney$^,$\CAASTRO, 
L.~J.~Greenhill\CfA,
P.~Hancock\Curtin$^,$\CAASTRO,
B.~J.~Hazelton\UW,
J.~N.~Hewitt\MIT,
L.~Hindson\Victoria,
D.~C.~Jacobs\ASU, 
M.~Johnston-Hollitt\Victoria,
A.~D.~Kapi\'{n}ska\UWA$^,$\CAASTRO,
H.-S.~Kim\UMelbourne$^,$\CAASTRO,
P.~Kittiwisit\ASU,
E.~Lenc\USydney$^,$\CAASTRO,
J.~Line\UMelbourne$^,$\CAASTRO,
A.~Loeb\CfA,
C.~J.~Lonsdale\Haystack, 
B.~McKinley\ANU$^,$\CAASTRO$^,$\UMelbourne,
S.~R.~McWhirter\Haystack,
D.~A.~Mitchell\CASS$^,$\CAASTRO, 
M.~F.~Morales\UW, 
E.~Morgan\MIT, 
J.~Morgan\Curtin,
A.~R.~Neben\MIT,
D.~Oberoi\Tata, 
S.~M.~Ord\Curtin$^,$\CAASTRO,
S.~Paul\RRI,
B.~Pindor\UMelbourne,
J.~C.~Pober\UW,
T.~Prabu\RRI, 
P.~Procopio\UMelbourne$^,$\CAASTRO,
J.~Riding\UMelbourne$^,$\CAASTRO,
N.~Udaya~Shankar\RRI, 
S.~Sethi\RRI,
K.~S.~Srivani\RRI,
L.~Staveley-Smith\UWA$^,$\CAASTRO,
R.~Subrahmanyan\RRI$^,$\CAASTRO, 
I.~S.~Sullivan\UW,
M.~Tegmark\MIT,
N.~Thyagarajan\ASU,
S.~J.~Tingay\Curtin$^,$\CAASTRO, 
C.~M.~Trott\Curtin$^,$\CAASTRO,
R.~L.~Webster\UMelbourne$^,$\CAASTRO, 
A.~Williams\Curtin, 
C.~L.~Williams\MIT,
C.~Wu\UWA,
J.~S.~Wyithe\UMelbourne$^,$\CAASTRO,
Q. Zheng\Victoria
\\
\ANU{}Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia \\
%\CAASTRO{}ARC Centre of Excellence for All-sky Astrophysics, Australian National University, Canberra, ACT 2611, Australia \\
\CAASTRO{}ARC Centre of Excellence for All-sky Astrophysics (CAASTRO) \\
\ASTRON{}Netherlands Institute for Radio Astronomy (ASTRON), PO Box 2, 7990 AA Dwingeloo, The Netherlands\\
\Curtin{}International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
\UWisc{}Department of Physics, University of Wisconsin--Milwaukee, Milwaukee, WI 53201, USA\\
\UW{}Department of Physics, University of Washington, Seattle, WA 98195, USA\\
\CASS{}CSIRO Astronomy and Space Science, Marsfield, NSW 2122, Australia\\
\SKASA{}SKA SA, 3rd Floor, The Park, Park Road, Pinelands, 7405, South Africa\\
\Rhodes{}Department of Physics and Electronics, Rhodes University, PO Box 94, Grahamstown, 6140, South Africa\\
\CfA{}Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA\\
\ASU{}School of Earth and Space Exploration, Arizona State University, Tempe, AZ 85287, USA\\
\USydney{}Sydney Institute for Astronomy, School of Physics, University of Sydney, NSW 2006, Australia\\
\Haystack{}MIT Haystack Observatory, Westford, MA 01886, USA\\
\RRI{}Raman Research Institute, Bangalore 560080, India\\
\MIT{}Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA 02139, USA\\
\UWA{}ICRAR, University of Western Australia, Crawley, WA 6009, Perth, Australia\\
\Victoria{}School of Chemical \& Physical Sciences, Victoria University of Wellington, Wellington 6140, New Zealand\\
\UMelbourne{}School of Physics, University of Melbourne, Parkville, VIC 3010, Australia\\
\Tata{}National Centre for Radio Astrophysics, Tata Institute for Fundamental Research, Pune 411007, India
%\UMichigan{}University of Michigan, Ann Harbor, MI 48109, USA
}
\jid{PASA}
\doi{10.1017/pas.\the\year.xxx}
\jyear{\the\year}
%Citations may be made using the natbib commands \citet{},\citep{} etc.
\usepackage[authoryear]{natbib}
\bibpunct{(}{)}{;}{a}{}{,}
\setlength{\bibsep}{0.3mm}
